---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```


```{r, eval=TRUE, echo=FALSE}
pgk_cov <- covr::package_coverage()
per_cov <- round(covr::percent_coverage(pgk_cov))
```


# icWGCNA

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
`r badger::badge_custom('codecov', paste0(per_cov,'%25'), color = 'green', url = 'https://covr.r-lib.org/')`
<!-- badges: end -->


## Overview

Iterative Correcting Weighted Gene Co-expression Network Analysis function for constructing a gene network from a gene expression matrix. The algorithm: 

    1. Constructs a signed wgcna network
    2. Drops correlated modules based on kurtosis
    3. Regresses out the largest community from the expression data
    4. Repeats steps 1-3 until a maximum number of communities or iterations is reached


Some differences from standard [WGNCA (Horvath/Langfelder)](https://bmcbioinformatics.biomedcentral.com/articles/10.1186/1471-2105-9-559):

  - Makes heavy use of [Rfast](https://cran.r-project.org/web/packages/Rfast/) to compute adjacencies and [topological overlap measure (TOM)](https://bmcbioinformatics.biomedcentral.com/articles/10.1186/1471-2105-9-559), which enables iterative network creation on > 20K features.
  - Uses [signed adjacency](https://bmcgenomics.biomedcentral.com/articles/10.1186/1471-2164-10-327) in order to avoid possible distortions of community signatures (eigengenes).
  - Iteratively regresses out strongest community in order to facilitate discovery of communities possibly obscured larger module(s).
  - Clustering does not focus on merging communities but dropping to identify strongest module(s), keeping communities with higher membership kurtosis.
  - In addition to Pearson correlation, there is an option for Spearman correlation as the base constructing adjacency matrix measure in order to enable robust application in RNA-seq and micro-array data. Future updates may include mutual information and other measures of similarity.


## Installation


Install the released version of icWGCNA from BMS RStudio Package Manager (BRAN):

```{r}
install.packages(
  "icWGCNA", 
  repos = "http://pm.rdcloud.bms.com:4242/bms-cg-biogit-bran/latest"
)
```

Or install the development version from BMS BioGit with:

```{r}
remotes::install_github(repo = "Systems-Immunology/icWGCNA", 
                        host = "https://biogit.pri.bms.com/api/v3")

```

Or:

```{r}
remotes::install_git(
  'https://biogit.pri.bms.com/Systems-Immunology/icWGCNA.git'
)
```


## Example

### Example Data

First we can use the [{UCSCXenaTools}](https://cran.r-project.org/web/packages/UCSCXenaTools/vignettes/USCSXenaTools.html) 
package to download an example mRNASeq dataset.

```{r}
luad <- UCSCXenaTools::getTCGAdata(project = "LUAD", 
                                   mRNASeq = TRUE, 
                                   mRNASeqType = "normalized",
                                   clinical = FALSE, 
                                   download = TRUE)

ex <- as.matrix(data.table::fread(luad$destfiles), rownames = 1)
```

### Main Results

Next we can run the main `icwgcna()` function

```{r}
library(icWGCNA)

results <- icwgcna(ex,   
                   expo = 6,
                   Method = "pearson",
                   q = 0.3,
                   maxIt = 10,
                   maxComm = 100,
                   corCut = 0.8,
                   covCut = 0.33,
                   mat_mult_method = "Rfast")


```

### Downstream Analysis

Finally, downstream analysis can be run on the Iterative Correcting Weighted Gene 
Co-expression Network Analysis results.

```{r}

compute_eigengene_matrix(ex, 
                         membership_matrix = results$community_membership, 
                         cutoff = 5,
                         pc_flag = TRUE)



pangDB <- data.table::fread(pangDB_link)
compute_panglaoDB_enrichment(results$community_membership,
                             K = 100,
                             memb_cut = 0.65,
                             pangDB = pangDB,
                             prolif = prolif_names)

```


## Code of Conduct
  
Please note that the icWGCNA project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
